Actuator line modeling of vertical-axis turbines

### 2016-05-13 paper.tex
Remove blade element discretization section

The actuator line model is based on the classical blade element theory combined
with a Navier--Stokes description of the flow field. The ALM treats turbine
blades as lines of blade elements, for which 2-D profile lift and drag
coefficients are given. For each blade element, relative flow velocity
$\vec{U}_\mathrm{rel}$ and angle of attack $\alpha$ are computed by adding the
vectors of relative blade motion $-\omega r$, where $\omega$ is the rotor
angular velocity and $r$ is the blade element radius, and the local inflow
velocity $\vec{U}_\mathrm{in}$, a diagram of which is shown in
Figure~\ref{fig:vectors}.

@@

\section{Blade element discretization}

In the ALM, a turbine is a collection of actuator lines, which themselves are
collections of actuator line elements (ALEs). The position of each ALE is a
point in space indicating its quarter-chord location. The element is further
defined by its chord direction vector, chord length, span direction vector, span
length, and velocity vector.

An actuator line is created from defined geometry points, between which ALE
parameters are interpolated linearly. This way, an actuator line can be defined
by fewer geometry points than element locations. For example, an AL with
straight planform boundaries---e.g. a straight or tapered wing---only needs two
geometry points to be fully defined. Figure~\ref{fig:AL-geom} shows and example
schematic of a tapered actuator line with three geometry points at the
half-chord locations and six total elements. Note that the middle geometry point
is technically redundant, but is shown for illustrative purposes. For actuator
lines that represent bluff bodies, e.g., shafts, the chord mount offset is set
to 1/4, such that the element location is centered along the line of geometry
points.

    \includegraphics[width=0.7\textwidth]{thesis_alm-geometry}

    \caption{Actuator line geometry. Filled circles indicate points where
    geometry is defined whereas squares indicate actuator line element
    quarter-chord locations. Chord mount offset is defined as the distance from
    an element's leading edge to each geometry point in chord lengths, which was
    0.5 for both rotors modeled in this study.}

    \label{fig:AL-geom}
\end{figure}

>>>>

The actuator line model is based on the classical blade element theory combined
with a Navier--Stokes description of the flow field. The ALM treats turbine
blades as lines of blade or actuator line elements, defined by their
quarter-chord location, and for which 2-D profile lift and drag coefficients are
known. For each blade element, relative flow velocity $\vec{U}_\mathrm{rel}$ and
angle of attack $\alpha$ are computed by adding the vectors of relative blade
motion $-\omega r$, where $\omega$ is the rotor angular velocity and $r$ is the
blade element radius, and the local inflow velocity $\vec{U}_\mathrm{in}$, a
diagram of which is shown in Figure~\ref{fig:vectors}.

@@
